The error in Bayesian phylogenetic reconstruction when speciation co-occurs

### 2018-12-04 article.tex
Put symbols and parameters in different tables

% Hypothesis: general
\item We hypothesize that the error made today, using BD tree priors,
increases with an increased number or stronger effect of multiple birth events.
This is straightforward: without multiple birth events or such event having
no effect, the MBD model falls back to a BD model. We expect larger
errors when we deviate more from the BD model's assumptions. 
Additionally, we hypothesize MBD having a stronger effect if the normal
speciation process is less pronounced. The more speciations are caused by the
BD process, there are relatively less multiple-birth events.
To put this hypothesis, H1, into an explicit equation, 
we expect the error made be correlated to the number 
of species created by the multiple-birth process over the total number 
of species created:

\begin{equation}
<e> = f(\frac{n_{taxa}^{MBD}}{n_{taxa}^{BD} + n_{taxa}^{MBD}})
\end{equation}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{table}
  \centering 
  \begin{tabular}{p{0.05\textwidth} p{0.6\textwidth} p{0.2\textwidth}}
    \hline
                          & Description & Value(s) \\
    \hline
    \hline
    $L_c$                 & MCMC chain length & $10^6$ \\
    $L_{sc}$              & MCMC sub-chain length & $10^4$ \\
    $\epsilon$            & relative error tolerance in marginal likelihood estimation & $10^{-13}$ \\
    \hline
  \end{tabular}
  \caption{
    Overview of the simulation parameters. 
  }
  \label{table:parameters}
\end{table}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

>>>>

From such phylogenies with different degrees of $s$, we measure the
inference error we make today, would nature follow such a phylogeny.
The inference error we make today is caused by the assumption of a BD process
and by inherent noise in this inference.

We expect
% Hypothesis: general
\item We hypothesize that the error made today, using BD tree priors,
increases with an increased number or stronger effect of multiple birth events.
This is straightforward: without multiple birth events or such event having
no effect, the MBD model falls back to a BD model. We expect larger
errors when we deviate more from the BD model's assumptions. 
Additionally, we hypothesize MBD having a stronger effect if the normal
speciation process is less pronounced. The more speciations are caused by the
BD process, there are relatively less multiple-birth events.
To put this hypothesis, H1, into an explicit equation, 
we expect the error made be correlated to the number 
of species created by the multiple-birth process over the total number 
of species created:

\begin{equation}
<e> = f(s)
\end{equation}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{table}
  \centering 
  \begin{tabular}{p{0.05\textwidth} p{0.6\textwidth} p{0.2\textwidth}}
    \hline
                          & Description\\
    \hline
    \hline
    $n_{\mathbb{M}}$      & Number of extinct and extant taxa created by a multiple-birth event \\
    $n_{\mathbb{B}}$      & Number of extinct and extant taxa created by a single-birth event \\
    $s$                   & Extent/strength of the multiple birth process \\
    $L_c$                 & MCMC chain length \\
    $L_{sc}$              & MCMC sub-chain length \\
    $\epsilon$            & relative error tolerance in marginal likelihood estimation \\
    \hline
  \end{tabular}
  \caption{
    Overview of the symbols. 
  }
  \label{table:symbols}
\end{table}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{table}
  \centering 
  \begin{tabular}{r l}
    \hline
                          & Value(s) \\
    \hline
    \hline
    $L_c$                 & $10^6$ \\
    $L_{sc}$              & $10^4$ \\
    $\epsilon$            & $10^{-13}$ \\
    \hline
  \end{tabular}
  \caption{
    Overview of the simulation parameters. 
  }
  \label{table:parameters}
\end{table}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
